### 2021-03-03 text/draft.tex
clean up
sklearn metrics test

Or put as question: what fraction of the subject terms suggested by
Annif are also in the native gold standard? The metric of precision is
implemented by \texttt{\_Analysis.get\_precision}.

@@

\begin{center} 
$\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}$
\end{center}

Put as question: what fraction of the subject terms in the gold standard
were suggested by Annif? The metric of recall is implemented by
\texttt{\_Analysis.get\_recall}.

@@

The metric of F1-score is implemented by \texttt{\_Analysis\_get\_f1}.

@@

I will now describe how the data foundation for the assessment was
created. There are three parameters that need to be distinguished(see
\protect\hyperlink{annif}{section ``Annif''}):

@@

For each configuration, the F1-score was computed for every item in the
sample data set. To do so, we call
\texttt{\_Analysis.super\_make\_metrics} on
\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
specifies the Annif configuration:

@@

Next, in order to be able to compare the F1-scores of the 100
configurations, a statistic (quartiles, IQR, mean) was computed for each
configuration by calling \texttt{\_Analysis.super\_make\_stats}, saving
the output as \texttt{/analysis/metrics\_stats.json}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{\_Analysis.super\_make\_stats()}
\end{Highlighting}
\end{Shaded}

@@

\leavevmode\hypertarget{ref-Roth.1993}{}%
Roth, Erwin, and Klaus Heidenreich. 1993. \emph{Sozialwissenschaftliche
Methoden: Lehr- Und Handbuch f{ü}r Forschung Und Praxis}. 3., v{ö}llig
{ü}berarbeitete und erweiterte Auflage. M{ü}nchen {[}etc.{]}: {R.
Oldenbourg Verlag}.

>>>>

Or put as question: what fraction of the subject terms suggested by
Annif are also in the native gold standard?

@@

\begin{center} 
$\text{Recall} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}$
\end{center}

Put as question: what fraction of the subject terms in the gold standard
were suggested by Annif?

@@

\hypertarget{implementation-1}{%
\paragraph{Implementation}\label{implementation-1}}

The above scoring metrics were implemented using the scikit-learn
machine learning library (Pedregosa et al. 2011). It is important to
note that each metric comes in three different flavors dubbed ``macro,''
``micro,'' and ``weighted'' respectively. In the macro flavor, the
metric represents simply the mean per class (i.e., correct or incorrect
suggestion). The weighted metric is the macro metric but each class is
weighted by its true positives. By contrast, a metric with the micro
flavor is computed globally over all true positives and false positives
respectively negatives.

@@

I will now describe how the data foundation for the assessment was
created. There are three parameters that need to be distinguished (see
\protect\hyperlink{annif}{section ``Annif''}):

@@

For each configuration, the F1-score (macro, micro and weighted) was
computed. To do so, we call \texttt{\_Analysis.super\_make\_metrics} on
\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
specifies the Annif configuration; a single file for analysis is saved
as \texttt{/analysis/metrics.json}:

@@

@@

\leavevmode\hypertarget{ref-Pedregosa.2011}{}%
Pedregosa, F., G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O.
Grisel, M. Blondel, et al. 2011. {``Scikit-Learn: Machine Learning in
Python.''} \emph{Journal of Machine Learning Research}, no. 12:
2825--30.
\url{https://www.jmlr.org/papers/volume12/pedregosa11a/pedregosa11a.pdf?source=post_page---------------------------}.

\leavevmode\hypertarget{ref-Roth.1993}{}%
Roth, Erwin, and Klaus Heidenreich. 1993. \emph{Sozialwissenschaftliche
Methoden: Lehr- Und Handbuch f{ü}r Forschung Und Praxis}. 3., v{ö}llig
{ü}berarbeitete und erweiterte Auflage. M{ü}nchen: {R. Oldenbourg
Verlag}.
